---
title: "Results"
---
# Results


## Gender Differences in Exhaustion and Engagement

To understand how burnout differs across genders, we compare the `Exhaustion` and `Engagement` scores.

```{r}
# Import libraries
library(ggplot2)
library(tidyr)
library(dplyr)

cleaned_data <- read.csv("OBI_cleaned.csv")

# Boxplot for Exhaustion by Gender
ggplot(cleaned_data, aes(x = as.factor(Gender), y = Exhaustion, fill = as.factor(Gender))) +
  geom_boxplot() +
  labs(title = "Exhaustion Scores by Gender",
       x = "Gender",
       y = "Exhaustion Score",
       fill = "Gender") +
  theme_minimal()

# Boxplot for Engagement by Gender
ggplot(cleaned_data, aes(x = as.factor(Gender), y = Engagement, fill = as.factor(Gender))) +
  geom_boxplot() +
  labs(title = "Engagement Scores by Gender",
       x = "Gender",
       y = "Engagement Score",
       fill = "Gender") +
  theme_minimal()
```
### Analysis
The boxplot for Engagement shows minimal differences between genders. We perform two-sample t-test to verify:

```{r}
t_test_engagement <- t.test(Engagement ~ Gender, data = cleaned_data)
t_test_engagement
```
**Results**:
Since the p-value is greater than 0.05, we fail to reject the null hypothesis, indicating no significant difference in Engagement scores between the 2 genders.



```{r}
# Interaction plot: Average Exhaustion by Age and Gender
summary <- cleaned_data %>%
  group_by(Age, Gender) %>%
  summarize(Avg_Exhaustion = mean(Exhaustion, na.rm = TRUE),
            Avg_Engagement = mean(Engagement, na.rm = TRUE))

ggplot(summary, aes(x = Age, y = Avg_Exhaustion, group = as.factor(Gender), color = as.factor(Gender))) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  labs(title = "Exhaustion by Age and Gender",
       x = "Age",
       y = "Average Exhaustion Score",
       color = "Gender") +
  theme_minimal()

ggplot(summary, aes(x = Age, y = Avg_Engagement, group = as.factor(Gender), color = as.factor(Gender))) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  labs(title = "Exhaustion by Age and Gender",
       x = "Age",
       y = "Average Exhaustion Score",
       color = "Gender") +
  theme_minimal()

```
### Analysis
The interaction plot shows that Exhaustion scores vary significantly across different ages for both genders. Notable observations:

..* Peaks occur at early and late career stages, possibly reflecting life and career pressures.
..* Gender differences are minimal overall, but specific age groups (e.g., late 20s, late 60s) exhibit noticeable differences.


```{r}

# Grouped bar plot: Average Engagement by Age and Gender
ggplot(summary, aes(x = Age, y = Avg_Engagement, fill = as.factor(Gender))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Engagement by Age and Gender",
       x = "Age",
       y = "Average Engagement Score",
       fill = "Gender") +
  theme_minimal()
```
### Analysis
The grouped bar plot provides some additional insights:

..* Engagement levels are relatively consistent across most ages but peak in younger participants.
..* Differences between genders are more significant in specific age groups, such as late 20s and 70+.
..* The variability in older age groups warrants further investigation, possibly due to life transitions or small sample sizes.

```{r}
write.csv(summary, "summary_results.csv", row.names = FALSE)
```

